%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Si}{Chen}
\address{Davis 301, University at Buffalo, Amherst, NY, US}
\mobile{(716) 335-8052} 
%%% Social
\email{quake0day@gmail.com}
\homepage{www.darlingtree.com}
\github{quake0day}
\linkedin{quake0day}
%%% Optionals
\position{Software Engineer}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {Climate Corporation.}
\letterdate{\today}
\lettertitle{Job Application for Software Engineer}
\letteropening{Dear Recipient,}
\letterclosing{Sincerely,}
%\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Si Chen~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
Hello, I'm Si Chen, a graduate student from computer science department. During my PhD study, I'm working as a Software Engineer developing smartphone sensing system and mobile security framework. I'm very excited to have an opportunity working as a Software Engineer in Climate Corporation.


\cvparagraph{Why Climate Corporation?}

I strongly believe I will be a good fit for this early-career engineer’s position due to the following reasons:
\begin{itemize}
\item I have a solid background on both computer science and electrical engineering.
\item I'm good at programming and have the ability for fast prototyping. 
\item I keep myself continuously learning new knowledge to enrich my capability.
\item I pursue a work environment fills up with creative colleagues and innovative ideas. Climate Corporation is able to offer me such an ideal career future. 
\end{itemize}
\cvparagraph{Why Me?}
As working in Climate Corporation, I can apply all my experiences to help you in developing robust system. I welcome the opportunity to discuss how my skills and experiences would contribute to Climate Corporation. Please feel free to contact me if you have any questions or require additional information.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
