\cvsection{Publications}
\begin{cventries}
\begin{itemize}
\item
\itemn{
\textbf{Si Chen}, Muyuan Li, Kui Ren, Xinwen Fu, Chunming Qiao, \emph{``Rise of the Indoor Crowd: Reconstruction of Building Interior View via Mobile Crowdsourcing,"} in \textbf{Proceedings of the 13th ACM Conference on Embedded Networked Sensor Systems (SenSys),} 2015.}
\item
\itemn{
\textbf{Si Chen}, Muyuan Li, Kui Ren, Chunming Qiao, \emph{``CrowdMap: Accurate Reconstruction of Indoor Floor Plan from Crowdsourced Sensor-Rich Videos,"} in \textbf{Proceedings of the 35th IEEE International Conference on Distributed Computing Systems (ICDCS),} 2015.}
%\item
%Si Chen, Muyuan Li, Zhan Qin, Kui Ren, \emph{``IndoorCrowd2D: Building Interior View Reconstruction via Mobile Crowdsourcing, "} in \textbf{Proceedings of the IEEE Conference on Computer Communications Workshops (INFOCOM WKSHPS),} 2015.
\item
\itemn{
Muyuan Li, Haojin Zhu, Zhaoyu Gao, \textbf{Si Chen}, Le Yu, Shangqian Hu, Kui Ren ,\emph{``All your location are belong to us: Breaking mobile social networks for automated user location tracking,"} in \textbf{Proceedings of the 15th ACM international symposium on Mobile ad hoc networking and computing (Mobihoc),} 2014.}
\item
\itemn{
Bingsheng Zhang, Qin Zhan, \textbf{Si Chen}, Muyuan Li, Kui Ren, Cong Wang, Di Ma, \emph{``PriWhisper: Enabling Keyless Secure Acoustic Communication for Smartphones,"} in \textbf{IEEE Internet of Things Journal,} 2014.}
\item
\itemn{
Eric Koski, \textbf{Si Chen}, Scott Pudlewski, Tommaso Melodia, \emph{"Network simulation for advanced HF communications engineering,"} in \textbf{Proceedings of the 12th International Conference on Ionospheric Radio Systems and Techniques (IRST),} 2012.}
\item
\itemn{
\textbf{Si Chen}, Lina Ling, Yuan Rongchang, Longqing Sun, \emph{"Classification Model of Seed Cotton Grade Based on Least Square Support Vector Machine Regression Method,"} in \textbf{Proceedings of the 6th IEEE International Conference on Information and Automation for Sustainability (ICIAfS),} 2012.}
\item
\itemn{
Rongchang Yuan, Zhengjiang Li, Si Chen, \emph{"Movement and deformation of virtual object based on argument passing method,"} in \textbf{Proceedings of the IEEE International Conference on Virtual Environments, Human-Computer Interfaces and Measurement Systems (VECIMS'12),} 2012.}
\item
\itemn{
Rongchang Yuan, Si Chen, Zhengjiang Li, Shengrong Lu, Li Wang, Haigan Yuan, \emph{"Simulation and Models on Control of Pests with Ozone in Greenhouses Plant,"} in \textbf{Proceedings of the IASTED International Conference on Modelling, Simulation, and Identification (MSI'2011),} 2011.}
\item
\itemn{
Rongchang Yuan, HaiganYuan, Si Chen, Longqing Sun, Feng Qin, Han Zhang, Yukun Zhu, Daokun Ma, \emph{"Research on the k-coverage local wireless network and its communication coordination mechanism design,"} in \textbf{Proceedings of the 5th International Conference on Computer and Computing Technologies in Agriculture (CCTA 2011)}, 2011}
\end{itemize}
\end{cventries}