% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[a4paper, 11pt]{article}




%-----------------------------------------------------------
%Margin setup
\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

%Fonts and Tweaks for XeLaTeX
\usepackage{fontspec}% provides font selecting commands 
\usepackage{xunicode}% provides unicode character macros 
\usepackage{xltxtra} % provides some fixes/extras
\defaultfontfeatures{Scale=MatchLowercase}
%\setmainfont[Mapping=tex-text]{Calibri}
%\setmainfont[Mapping=tex-text]{Qlassik Medium}
%\setmainfont[Mapping=tex-text]{Gill Sans MT}
\setmainfont[Mapping=tex-text]{Trebuchet MS}
\newfontfamily\notefont{Times}
\newfontfamily\texfont{Baskerville}
%\setsansfont[Mapping=tex-text]{Skia}
%\setmonofont{Courier}
%-----------------------------------------------------------




%\usepackage{fullpage}
\usepackage{textcomp}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


\usepackage[svgnames]{xcolor}           % xcolor package
\definecolor{shadecolor}{gray}{0.90}    % Background color of section bars
%Styling Itemizations

\usepackage{pifont}
\usepackage{bbding}
\renewcommand{\labelitemi}{*}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}


\newcommand{\ressection}[1]
{\fcolorbox{black}{shadecolor}{\vbox{\hsize 0.98\textwidth \textbf{\mbox{~}{\@ \large #1} \vphantom{p\^{E}}}}}}
 
% Usage : ressubsection{item1}{comment1}{item2}{comment2}
\newcommand{\ressubsection}[4]
{
\begin{tabular*}{0.9\textwidth}{l@{\extracolsep\fill}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}
}
 
% Usage : resrowitemlr{item}{comment}
\newcommand{\resrowitemlr}[2]
{
\begin{tabular*}{0.9\textwidth}{l@{\extracolsep\fill}r}
    \textbf{#1} & #2 \\
\end{tabular*}
}
 

%-----------------------------------------------------------


\begin{document}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large \fontsize{26}{26} {\notefont Si Chen}}  & \Phone\@ (716)335-8052\\
79 Raintree Island Apt.11& \Envelope\@  schen23@buffalo.edu \\
Tonawanda, NY 14150 \\
\end{tabular*}
\\
\vspace{0.1in}

\ressection{Education}
\begin{itemize}
\item
	\ressubheading{University at Buffalo - SUNY}{Buffalo, NY}{Ph.D., Computer Science (GPA 3.8)}{Sep. 2012 - Present}
	\begin{itemize}
		\resitem{Research Assistance in Ubiquitous Security and Privacy Research Laboratory
(UbiSeC Lab), \\ 
Advisor: Dr. Kui Ren}
		\resitem{Relevant courses: Applied Cryptography and Computer Security, Wireless Network Security, Theory of Computation, Modern Network Concept, Wireless Networking and Mobile Computing}
	\end{itemize}
	
\item
	\ressubheading{University at Buffalo - SUNY}{Buffalo, NY}{M.S., Electrical Engineering (GPA 3.8)}{Sep. 2010 - May. 2012}
	\begin{itemize}
	\resitem{Research Assistance in Wireless Networks and Embedded Systems Lab (WINES Lab), \\
	 Advisor: Dr. Tommaso Melodia}
		\resitem{Relevant courses: Multimedia Wireless Sensor Network, Principle of Information Theory and Coding, Optimization of Wireless Network}
	\end{itemize}

\item
	\ressubheading{China Agricultural University}{Beijing, China}{B.S., Measuring \& Control Technology and Instrumentations}{2006-2010}
	\begin{itemize}
		\resitem{Graduated with Honors, Top 100 Excellent Graduate Theses award winner}
		%\resitem{Relevant courses: Application of MATLAB, C Programming Language, Principles of Microcomputer and Interface Technology, Signal Processing, Sensor and Detecting circuits, Practical Image Processing, Computer Measurement \& Control Technology, Principle \& Application of Single Chip Microcomputer}
	\end{itemize}

\end{itemize}

\ressection{Publications}
\begin{itemize}
\item 
Si Chen, Muyuan Li, Kui Ren, Xinwen Fu, Chunming Qiao, \emph{``Rise of the Indoor Crowd: Reconstruction of Building Interior View via Mobile Crowdsourcing,"} in \textbf{Proceedings of the 13th ACM Conference on Embedded Networked Sensor Systems (SenSys 2015),} 2015.
\item 
Si Chen, Muyuan Li, Kui Ren, Chunming Qiao, \emph{``CrowdMap: Accurate Reconstruction of Indoor Floor Plan from Crowdsourced Sensor-Rich Videos,"} in \textbf{Proceedings of the 35th IEEE International Conference on Distributed Computing Systems (ICDCS'15),} 2015.
\item
Si Chen, Muyuan Li, Zhan Qin, Kui Ren, \emph{``IndoorCrowd2D: Building Interior View Reconstruction via Mobile Crowdsourcing, "} in \textbf{Proceedings of the IEEE Conference on Computer Communications Workshops (INFOCOM WKSHPS),} 2015.
\item 
Muyuan Li, Haojin Zhu, Zhaoyu Gao, Si Chen, Le Yu, Shangqian Hu, Kui Ren ,\emph{``All your location are belong to us: Breaking mobile social networks for automated user location tracking,"} in \textbf{Proceedings of the 15th ACM international symposium on Mobile ad hoc networking and computing (Mobihoc'14),} 2014.
\item 
Bingsheng Zhang, Qin Zhan, Si Chen, Muyuan Li, Kui Ren, Cong Wang, Di Ma, \emph{``PriWhisper: Enabling Keyless Secure Acoustic Communication for Smartphones,"} in \textbf{IEEE Internet of Things Journal,} 2014.
\item 
Si Chen, Muyuan Li, Kui Ren, \emph{``The power of indoor crowd: Indoor 3D maps from the crowd,"} in \textbf{Proceedings of the IEEE Conference on Computer Communications Workshops (INFOCOM WKSHPS),} 2014.
\item 
Si Chen, Muyuan Li, Zhan Qin, Bingsheng Zhang, Kui Ren, \emph{``AcousAuth: An acoustic-based mobile Application for user authentication,"} in \textbf{Proceedings of the IEEE Conference on Computer Communications Workshops (INFOCOM WKSHPS),} 2014.
\item 
Muyuan Li, Si Chen, Kui Ren, \emph{``Enabling private and non-intrusive smartphone calls with LipTalk,"} in \textbf{Proceedings of the IEEE Conference on Computer Communications Workshops (INFOCOM WKSHPS),}  2014.
\item 
Eric Koski, Si Chen, Scott Pudlewski, Tommaso Melodia, \emph{"Network simulation for advanced HF communications engineering,"} in \textbf{Proceedings of the 12th International Conference on Ionospheric Radio Systems and Techniques (IRST2012),} 2012.
\item 
Si Chen, Lina Ling, Yuan Rongchang, Longqing Sun, \emph{"Classification Model of Seed Cotton Grade Based on Least Square Support Vector Machine Regression Method,"} in \textbf{Proceedings of the IEEE International the 6th International Conference on Information and Automation for Sustainability (ICIAfS'12),} 2012.
\item 
Rongchang Yuan, Zhengjiang Li, Si Chen, \emph{"Movement and deformation of virtual object based on argument passing method,"} in \textbf{Proceedings of the IEEE International Conference on Virtual Environments, Human-Computer Interfaces and Measurement Systems (VECIMS'12),} 2012.
\item
Rongchang Yuan, Si Chen, Zhengjiang Li, Shengrong Lu, Li Wang, Haigan Yuan, \emph{"Simulation and Models on Control of Pests with Ozone in Greenhouses Plant,"} in \textbf{Proceedings of the IASTED International Conference on Modelling, Simulation, and Identification (MSI'2011),} 2011.
\item
Rongchang Yuan, HaiganYuan, Si Chen, Longqing Sun, Feng Qin, Han Zhang, Yukun Zhu, Daokun Ma, \emph{"Research on the k-coverage local wireless network and its communication coordination mechanism design,"} in \textbf{Proceedings of the 5th International Conference on Computer and Computing Technologies in Agriculture (CCTA 2011)}, 2011
\end{itemize}

\ressection{Selected Research Projects}

\begin{itemize}
\item
	\ressubheading{IndoorCrowd}{Buffalo, NY}{Project Leader, Ubiquitous Security and Privacy Research Laboratory
(UbiSeC Lab)}{Jun. 2013 - Present}
	\begin{itemize}
		\resitem{Designed and Implemented a smartphone empowered cloud-based crowdsourcing system for large-scale indoor scene reconstruction. }
	\end{itemize}


\item
	\ressubheading{AcousAuth}{Buffalo, NY}{Project Leader, Ubiquitous Security and Privacy Research Laboratory
(UbiSeC Lab)}{Jun. 2013 - Oct. 2013}
	\begin{itemize}
		\resitem{Designed and Implemented a smartphone empowered personal authentication system exploiting keyless acoustic communication. }
                 \resitem{Winner of the 19th Annual International Conference on Mobile Computing and Networking (MobiCom'13) App Competition Finalists (top 10).}
	\end{itemize}


\item
	\ressubheading{Ground Wave Simulator}{Buffalo, NY}{Project Leader, Wireless Networks and Embedded Systems Laboratory (WINES Lab)}{2011 - May. 2012}
	\begin{itemize}
		\resitem{Implemented an online ground wave simulation system based on NS-2 open source network simulator, GRWAVE and VOACAP Software to simulate advanced high frequency (HF) network.}
	\end{itemize}
	
\item
	\ressubheading{Cognitive Radio Framework}{Buffalo, NY}{Wireless Networks and Embedded Systems Laboratory (WINES Lab)}{2011 - Jan. 2012}
	\begin{itemize}
		\resitem{Implemented TCP/IP protocol into GNU Radio testbed USRP2}
		\resitem{GNU Radio co-operative setup}
		%\resitem{Establish Bridge and framework abstraction for the cognitive radio framework}
	\end{itemize}
	
\item
	\ressubheading{Intellectualized Greenhouse Measuring \& Control System}{Beijing, China}{Project Leader, National University Student Innovation Program}{2009 - May. 2010}
	\begin{itemize}
		\resitem{Used CC2430 wireless node and Zigbee stack (Z-stack) to measure and control a greenhouse model's humidity and temperature.}
		\resitem{Used Python, PHP, Javascript (jQuery), MySQL and C to create a realtime B/S System.}
		\resitem{Designed a PCB with controllers that can use CC2430 with computer to remote control the greenhouse model.}
		\resitem{Designed and built a greenhouse model.}
		\resitem{Implemented PHP reflection mechanism to create a plugin system for further system enhancement.}
	\end{itemize}



%\item
%Rongchang Yuan, Si Chen, Zhengjiang Li, Shengrong Lu, Li Wang, Haigan Yuan ,\emph{"Simulation and Models on Control of Pests with Ozone in Greenhouses Plant,"} in \textbf{ IASTED International Conference on Modelling, Simulation, and Identification (MSI'2011)}, Pittsburgh, USA, November 2011.
%\item
%Rongchang Yuan, HaiganYuan, Si Chen, Longqing Sun, Feng Qin, Han Zhang, Yukun Zhu, Daokun Ma,\emph{"Research on the k-coverage local wireless network and its communication coordination mechanism design,"} in \textbf{the Fifth International Conference on Computer and Computing Technologies in Agriculture (CCTA2011)}, Beijing, China, October 2011
\end{itemize}
\ressection{Previous Work Experience and Internships}
\begin{itemize}
\item
	\ressubheading{University at Buffalo - SUNY}{Buffalo, US}{Research Assistant}{Aug. 2013 - Aug. 2015}
	%\begin{itemize}
	%	\resitem{Used Python (Matplotlib), Javascript (jQuery) and PHP with MySQL to build an UNIX cluster administration system}
	%	\resitem{Designed and implemented an algorithm to calculate daily hottest words from Weibo (Chinese twitter) search log in Python}
	%	\resitem{Created an usage frequency indicator to show Weibo's  current usage frequency in different areas using Python, C, PHP with MySQL, Javascript }
	% \end{itemize}
\item
	\ressubheading{Sina Weibo (China)}{Beijing, China}{Application Dev Engineer (Internship)}{Apr. 2010 - July. 2010}
	\begin{itemize}
		\resitem{Used Python (Matplotlib), Javascript (jQuery) and PHP with MySQL to build an UNIX cluster administration system}
	%	\resitem{Designed and implemented an algorithm to calculate daily hottest words from Weibo (Chinese twitter) search log in Python}
		\resitem{Created an usage frequency indicator to show Weibo's  current usage frequency in different areas using Python, C, PHP with MySQL, Javascript }
	\end{itemize}
\item
	\ressubheading{ASSE/WH China}{Beijing, China}{Website Developer and Website Administrator (Part-time job)}{Oct. 2007- Feb. 2008}
	\begin{itemize}
		\resitem{Re-constructed company's website using Mambo CMS System}
		\resitem{Built an online registration system using PHP and MySQL}
	\end{itemize}
%\item
	%\ressubheading{ASSE/WH China}{Beijing, China}{Website Developer and Website Administrator (Part-time job)}{Oct. 2007- Feb. 2008}
	%\begin{itemize}
		%\resitem{Re-constructed company's website using Mambo CMS System}
		%\resitem{Built an online registration system using PHP and MySQL}
	%\end{itemize}


\end{itemize}

\ressection{Extracurriculum Works}
	\begin{itemize}
		\resitem{Used SigOps uBoot System (UIUC), C, Assembly to create my own operating system \textquotesingle Quake\textquotesingle }
		\resitem{Used Python, MySQL to create a program which helps me to increase Weibo followers automatically}
		\resitem{Used Python, jQuery, PHP, MySQL to build an on-line GPA Calculate System}
		\resitem{Used Python, C++, Sed, PHP, MySQL and Javascript to design an Automatic Tests Score SMS Notifier}
		\resitem{Used CC2430 wireless single chip microcomputer and TinyOS embedded system, PHP, MySQL, C, Shell Script to create an Amphibian \& Reptiles Aquarium Monitoring System}
		\resitem{Used Google Map API, Javascript, HTML to design an on-line alumni catalog}
		\resitem{Co-founder and technique advisor of the Future Engineers Association (FEA) }
	\end{itemize}
	
\ressection{Honors and Awards}

	\begin{tabular*}{6.7in}{l@{\extracolsep{\fill}}r}
	\\
		\@ \@  \@ \@ \@ \@  \@ \@ Top 100 Excellent Graduate Theses in China Agricultural University & 2010\\
		\@ \@  \@ \@ \@ \@  \@ \@    Excellent Graduate Award in China Agricultural University & 2010\\
		\@ \@  \@ \@ \@ \@  \@ \@     National University Student Innovation Program Award (\$3200) & 2009-2010\\
		\@ \@  \@ \@ \@ \@  \@ \@    Undergraduate Research Program Award (\$500) & 2007-2008\\
		\@ \@  \@ \@ \@ \@  \@ \@    Third Prize of International Interdisciplinary Contest in Modeling (ICM) & 2009\\
		\@ \@  \@ \@ \@ \@  \@ \@    Third Prize of Scholarship for Excellent Academic Performance (\$100) & 2007,2008,2009\\
		\@ \@  \@ \@ \@ \@  \@ \@    Awarded twice ``The best debater"  title in debate competitions & 2006,2007\\
		\\
\end{tabular*}


	
\ressection{Skills}

\begin{description}
\item[\@ \@  \@ \@ \@ \@  \@ \@ Programming Languages:]
Python, C,  {\texfont \TeX}, Javascript, Shell, SQL, PHP, HTML, Perl, Java, Haskell, Assembly
\item[\@ \@  \@ \@ \@ \@  \@ \@ Operating Systems:]
Linux (Gentoo Linux), OS X, Windows, FreeBSD
\item[\@ \@  \@ \@ \@ \@  \@ \@ Applications:]
MATLAB, Vim, Cadence Virtuoso, {\texfont \LaTeX}, Photoshop, MS Office
\item[\@ \@  \@ \@ \@ \@  \@ \@ Framework:]
Android Development Framework (JAVA), GNU Radio (Python), Django (Python), Web.py (Python), jQuery(Javascript)
\item[\@ \@  \@ \@ \@ \@  \@ \@ Miscellaneous:]
Rapid Prototyping Ability, Excellent Troubleshooting and Debugging Skills, Good Problem Solving Skills. 
\end{description}


%\ressection{Interests}

%\begin{description}
%\item[Academic:] Wireless Sensor and Actor networks, Cognitive Radio/Dynamic Spectrum Access Networks, Optimization of wireless communication networks
%\item[Sports:] Jogging and swimming
%\item[Computers:]  Enjoy using and learning Linux systems, Building electronics projects, and writing small tool-kits using Python
%\item[Membership:] Student member of Institution of Mechanical Engineers (IMechE) in 2009-2010
%\item[Other:] Reading novels, Raising pets
%\end{description}

\end{document}
